Ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2017-08-25 manuscript/usses_water_ms.Rmd
removes all old text

<!---
Ecosystems worldwide are projected to experience either wetter or drier conditions in the future [@Zhang2007; @Greve2014].
This has important implications for ecosystem functioning because mean annual net primary productivity (ANPP) positively covaries with mean annual precipitation across ecosystems [@Sala1988; @Huxman2004] and interannual responses of ANPP are linked to interannual variability in precipitation within ecosystems [@Lauenroth1992; @Hsu2012; @Gherardi2015a].
To predict how ecosystems might respond to extreme precipitation levels, we need to understand whether ecosystems tend to follow temporal trends, which assume relatively constant plant community composition, or spatial trends, which allow community composition to shift [@Wilcox2016].
--->

@@

<!---
\begin{align}
\mu_{j(k(t))} &= \beta_{0,j(k)} + \beta_{1,j(k)}x_{k(t)} + \gamma_t, \\
y_{j(k(t))} &\sim \text{Normal} \left(\mu_{j(k(t))}, \sigma^2_{k} \right),
\end{align}
---->

@@

<!----
is the intercept for plot *j* associated with treatment *k*, $\beta_{1,j(k)}$ is the slope term for the effect of soil moisture for plot *j* associated with treatment *k*, $\gamma_t$ is the intercept offset for year *t*, and $\sigma^2_k$ is the process variance for treatment *k*.
Data include the standardized log(ANPP) observations $\left( y_{j(k(t))} \right)$ and soil moisture ($x_{k(t)}$).

The intercept and slope terms are modeled hierarchically to account for the non-independence of observations across years within plots and to allow us to test the hypothesis that our treatments alter the ANPP-soil moisture relationship.
Thus, our multi-level model has three grouping levels for coefficients, representing the nested structure of the data: (i) overall coefficients, (ii) treatment coefficients, and (iii) plot coefficients.
Each subsequent level is drawn from the distribution of coefficients at the previous level, meaning plot-level coefficients are drawn from treatment-level coefficients, which are drawn from overall coefficients.
We also include a covariance structure among the intercept and slope at each level.
Formally, our hierarchical structure is as follows, where we drop the intercept (0) and slope (1) subscripts and instead refer to a vector of coefficients, $\boldsymbol{\beta}$:

\begin{align}
\boldsymbol{\beta}_{j(k)} &\sim \text{MVN} \left( \boldsymbol{\beta}_k, \boldsymbol{\Sigma}(k) \right), \\
\boldsymbol{\beta}_{k} &\sim \text{MVN} \left( \boldsymbol{\beta}, \boldsymbol{\Sigma}  \right), \\
\boldsymbol{\beta} &\sim \text{Normal} \left( 0, 1 \right),
\end{align}

\noindent{}where $\boldsymbol{\beta}_{j(k)}$ is the vector of regression coefficients (intercept and slope) for plot *j* associated with treatment *k*, $\boldsymbol{\beta}_{k}$ is the vector of coefficients for each treatment, and $\boldsymbol{\beta}$ is the vector of overall coefficients.
The plot- and treatment-level coefficients are drawn from multivariate normal distributions with covariance matrix $\boldsymbol{\Sigma}$.
For the plot-level coefficients, each treatment has its own variance-covariance matrix (i.e., $\boldsymbol{\Sigma}(k)$).
The overall coefficients are drawn from a normal prior with mean 0 and standard deviation 1.
The random year effects ($\boldsymbol{\gamma}$) are drawn from a normal prior with mean 0 and standard deviation $\sigma_{\text{year}}$, which was drawn from a weibull distribution.
A full description of model is in Appendix 2.
---->

@@

<!---
```{r get_results, echo=FALSE}
betas <- read.csv("../results/beta_summaries.csv")
```
--->

@@

<!---
The results of our five year experiment in a sagebrush steppe conform to the first of our four predictions: neither ecosystem functional response nor community composition changed with chronic alteration in water availability (Fig. 1, top left).
--->

@@

The weaker soil moisture-ANPP relationship we observed for the irrigation treatment, evidenced by the less positive slope relative to controls (Fig. 3A, right panel), has three non-exclusive explanations.
First, species' biomass production may have hit physiological thresholds and/or become limited by other factors, such as nitrogen availability [@LeBauer2008].
\pba{PETER: DO WE KNOW ANYTHING ABOUT NITROGEN AT USSES? WANT TO ADD A SENTENCE HERE ABOUT HOW LIKELY THIS IS...}
Second, the less positive slope could be another indicator of bet hedging in this community.
Avoiding high biomass production in wet years could benefit species in the long run if climate conditions are variable.
Third, the less positive slope may be a statistical artifact due the variability of ANPP within years and our low sample size.

@@

<!---
\newpage{}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{../figures/glmm_yeardiffs.png}
  \caption{Posterior distributions of random year effects (intercept offsets). Kernel bandwidths of posterior densities were adjusted by a factor of 5 for visual clarity.}
\end{figure}
--->

>>>>

@@

@@

@@

@@

@@

The weaker soil moisture-ANPP relationship we observed for the irrigation treatment, evidenced by the less positive slope relative to controls (Fig. 3A, right panel), has three non-exclusive explanations.
First, species' biomass production may have hit physiological thresholds and/or become limited by other factors, such as nitrogen availability [@LeBauer2008].
\pba{PETER: DO WE KNOW ANYTHING ABOUT NITROGEN AT USSES? WANT TO ADD A SENTENCE HERE ABOUT HOW LIKELY OR UNLIKEL THIS IS...}
Second, the less positive slope could be another indicator of bet hedging in this community.
Avoiding high biomass production in wet years could benefit species in the long run if climate conditions are variable.
Third, the less positive slope may be a statistical artifact due the variability of ANPP within years and our low sample size.

@@

### 2017-08-25 manuscript/usses_water_ms.tex
removes all old text

The weaker soil moisture-ANPP relationship we observed for the
irrigation treatment, evidenced by the less positive slope relative to
controls (Fig. 3A, right panel), has three non-exclusive explanations.
First, species' biomass production may have hit physiological thresholds
and/or become limited by other factors, such as nitrogen availability
\citep{LeBauer2008}.
\pba{PETER: DO WE KNOW ANYTHING ABOUT NITROGEN AT USSES? WANT TO ADD A SENTENCE HERE ABOUT HOW LIKELY THIS IS...}
Second, the less positive slope could be another indicator of bet
hedging in this community. Avoiding high biomass production in wet years
could benefit species in the long run if climate conditions are
variable. Third, the less positive slope may be a statistical artifact
due the variability of ANPP within years and our low sample size.

@@

\bibliography{/Users/atredenn/Dropbox/Bibliography/usses_water.bib}

>>>>

The weaker soil moisture-ANPP relationship we observed for the
irrigation treatment, evidenced by the less positive slope relative to
controls (Fig. 3A, right panel), has three non-exclusive explanations.
First, species' biomass production may have hit physiological thresholds
and/or become limited by other factors, such as nitrogen availability
\citep{LeBauer2008}.
\pba{PETER: DO WE KNOW ANYTHING ABOUT NITROGEN AT USSES? WANT TO ADD A SENTENCE HERE ABOUT HOW LIKELY OR UNLIKEL THIS IS...}
Second, the less positive slope could be another indicator of bet
hedging in this community. Avoiding high biomass production in wet years
could benefit species in the long run if climate conditions are
variable. Third, the less positive slope may be a statistical artifact
due the variability of ANPP within years and our low sample size.

@@

\bibliography{~./usses_water.bib}
